Bootstrapping Multi-atlas Segmentation Using Multiple Automatically Generated Templates for the Segmentation of the Whole Hippocampus and Subfields

### 2014-01-02 paper.Rnw
Adding updated WA xval experiment

wa.s = ddply(wa.xval.error, c('region'), function(df) {
  with(df,data.frame(
    m_res = mean(resampled,na.rm=T), sd_res = sd(resampled,na.rm=T),
    m_bravo = mean(mb_bravo,na.rm=T), sd_bravo = sd(mb_bravo,na.rm=T),
    m_mb_res = mean(mb_0.9mm,na.rm=T), sd_mb_res = sd(mb_0.9mm,na.rm=T)))})
@

>>>>

wa.s = ddply(wa.xval.error, c('region'), function(df) {
  with(df,data.frame(
    m_res = mean(resampled,na.rm=T), sd_res = sd(resampled,na.rm=T),
    m_bravo = mean(mb_bravo,na.rm=T), sd_bravo = sd(mb_bravo,na.rm=T),
    m_mb_res = mean(mb_0.9mm,na.rm=T), sd_mb_res = sd(mb_0.9mm,na.rm=T)))})

wa.n.sim = read.csv('data/winterburn.xval.similarity.csv')
wa.n.vol = read.csv('data/winterburn.xval.volumes.csv')
winterburn = read.csv('data/winterburn.volumes.csv')

wa.n.vol.melt = melt(wa.n.vol, id.vars=c('atlases','subject','res'))
winterburn.melt = melt(winterburn, id.vars=c('subject','res'))
winterburn.cast = dcast(winterburn.melt, subject + variable ~ res)
wa.n.all.vols = merge(wa.n.vol.melt, winterburn.cast, by=c('subject','variable'))
#wa.n.vols.mean = ddply(wa.n.all.vols,c('subject','variable'),function (df) {
#  data.frame(
#    mb=mean(df$value),
#    X.3=mean(df$'0.3'),
#    X.9=mean(df$'0.9'))})

levels(wa.n.all.vols$variable) <-list(
  "CA1"="X1", "CA1"="X101", "Subiculum"="X2","Subiculum"="X102", 
  "CA4/DG"="X4","CA4/DG"="X104", "CA2/CA3"="X5","CA2/CA3"="X105", 
  "SR/SL/SM"="X6","SR/SL/SM"="X106")

wa.n.all.vols$diff = wa.n.all.vols$'0.9' - wa.n.all.vols$value
wa.n.all.vols$mean = (wa.n.all.vols$'0.9' + wa.n.all.vols$value)/2

wa.n.xval.bland.limits = ddply(wa.n.all.vols,c("variable"),function(df) {
  data.frame(y = mean(df$diff,na.rm=T) + c(-1.96,0,2) * sd(df$diff,na.rm=T))
})
@

\begin{figure}[h!]
<<fig:WAxval-kappa>>=
wa.n.sim$label = as.factor(wa.n.sim$label)
levels(wa.n.sim$label) <-list(
  "CA1"=1, "CA1"=101, "Subiculum"=2,"Subiculum"=102, 
  "CA4/DG"=4,"CA4/DG"=104, "CA2/CA3"=5,"CA2/CA3"=105, 
  "SR/SL/SM"=6,"SR/SL/SM"=106)

# kappa vs. region
ggplot(wa.n.sim, aes(x=as.factor(label),y=k)) + 
  geom_boxplot() + 
  xlab("Subregion") + 
  ylab("Dice's Similarity Coefficient (DSC)")
@
  \caption{Similarity of \mb{} segmentation of subregions and resampled Winterburn atlas labels at $0.9mm^3$ voxel resolution over all folds of a leave-one-out cross validation.}
\end{figure}

\begin{figure}[h!]
<<fig:WAxval-Bland-Altman>>=
ggplot(wa.n.all.vols, aes(x=mean, y=diff)) + 
  facet_wrap(~variable, ncol=3, scales='free') + 
  geom_smooth(method="lm", formula=y~x, fullrange=T, se=F) + 
  geom_point(size=1) +  
  geom_hline(aes(yintercept = y), linetype="dashed", colour="brown",
             data=wa.n.xval.bland.limits, size=0.3, alpha=0.5) + 
  geom_text(aes(y = y, x=Inf, label=round(y,0)), colour="black", 
             data = wa.xval.bland.limits, hjust=1.1,vjust=-0.8, size=2.5) + 
  xlab(expression('Mean of resampled and \\mb subregion volume ' (mm^3))) + 
  ylab(expression('Difference between manual and \\mb subregion volume ' (mm^3))) + 
  scale_color_discrete(name="") + 
  theme(legend.direction = "horizontal", legend.position = "bottom", 
        axis.text.y = element_text(angle = 90, hjust=0.5), 
        axis.text = element_text(size = 8))
@
  \caption{Bland-Altman plots across all folds of Winterburn atlas cross validation.}
\end{figure}
